I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-23 Paper/proofs.tex
fix typos and others

	\begin{lemma}
		If a DNN has no compensating pair, then it also does not have weak compensating pair.
	\end{lemma}

	\begin{proof}
		If it has a weak compensating pair of two path, $P_1,P_2$, then there exists a segment in two paths starting from the same node and end with the same node, but the weight along two segment have different signs. And this will also be a compensating pair. \qed
	\end{proof}

@@

			In this section, we will prove theorem \ref{th2}. We will prove it by proving the following theorem:

@@

				Suppose $\mathcal{N}$ is a DNN with $\ReLU$ as the unique activation functions and with a unique output node $z$.

				Using MILP, if every nodes $b$ in any compensating pair
				$(\pi,\pi')$ (except the start node and end node) is encoded as a binary/integer variable (opened), then the upper and lower 
				bounds computed by MILP are the exact maximal and minimal value of $z$.
			\end{theorem}

@@

					\end{enumerate}
					That is, $a_k$ is not a source of a weak compensating pair. 	We write $A_{pure}$ by $I$ for short.
					\item $a_k \in A_{open}$ if $a_k \notin A_{pure}$, that is there exists two paths $\pi,\pi'$ from $k$, 
					one with positive and one with negative weight. 	We write $A_{open}$ by $J$ for short.
				\end{itemize}
			\end{definition}

			\begin{lemma} \label{lem:open_node_2}
				A node $b$ in the hidden layer will not be in a weak compensating path if and only if one of the following two happens:
				\begin{enumerate}
					\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $weight({bz})=0$ to denote this case, or
					\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $weight({a_jb})=0$ to denote this case.
				\end{enumerate}

@@

			We denote $B_{zero}$ the set of such nodes $b$ that case 1 holds, and denote $B_{pure}$ the of such nodes $b$ that case 2 holds but case 1 does not hold.	We denote $B_{open}$ the set of all nodes $b$ in a compensating path.

@@

			\begin{lemma}\label{lem:subnetwork}
				$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward: if $b$ is connected to $c$ and $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$. We call this sub-network $D_I$. In $D_I$, there is no compensating pair.
			\end{lemma}

@@

			Recall the sign function of nodes from Definition \ref{sign_of_nodes}. Because now we allow compensating paths, the sign function is no longer total (no longer defined on all nodes).

@@

			\begin{lemma}
				If $c$ is in the next layer after $b$, $S(c)\neq 0, S(b)$ are both defined, and $W_{bc}\neq 0$, then $W_{bc}S(c)=S(b)$.
			\end{lemma}

>>>>

	\begin{lemma}
		If a DNN has no compensating pair, then it also does not have weak compensating pair from an input node to the output node.
	\end{lemma}

	\begin{proof}
		If it has a weak compensating pair of two paths, $P_1,P_2$, then there exists a segment in two paths starting from the same node and end with the same node, but the weight along two segment have different signs. And this will also be a compensating pair. \qed
	\end{proof}

@@

			In this section, we will prove theorem \ref{th2}. We will prove it by proving the following weak theorem:

@@

				Suppose $\mathcal{D}$ is a DNN with $\ReLU$ as the unique activation functions and with a unique output node $z$.

				Using MILP, if every nodes $b$ in any weak compensating pair
				$(\pi,\pi')$ (except the start node and end node) is encoded as a binary/integer variable (opened), then the upper and lower 
				bounds computed by MILP are the exact maximal and minimal value of $z$.
			\end{theorem}

@@

					\end{enumerate}
					That is, $a_k$ is not a source of a weak compensating pair. 	We write $A_{pure}$ by $I$ for short.
					\item $a_k \in A_{open}$ if $a_k \notin A_{pure}$, that is there exists two paths $\pi,\pi'$ from $a_k$, 
					one with positive and one with negative weight. 	We write $A_{open}$ by $J$ for short.
				\end{itemize}
			\end{definition}

			\begin{lemma} \label{lem:open_node_2}
				A node $b$ in a hidden layer will not be in a weak compensating path if and only if one of the following happens:
				\begin{enumerate}
					\item Any path from $b$ to the output node $z$ has a weight $0$, and we use $weight({bz})=0$ to denote this case, or
					\item For every input node $a_j\in J$, every path from $a_j$ to $b$ has a weight of $0$. We use $weight({a_jb})=0$ to denote this case.
				\end{enumerate}

@@

			We denote $B_{zero}$ the set of such nodes $b$ that case 1 holds, and denote $B_{pure}$ the of such nodes $b$ that case 2 holds but case 1 does not hold.	We denote $B_{open}$ the set of all nodes $b$ in a weak compensating path.

@@

			\begin{lemma}\label{lem:subnetwork}
				$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward. That is to say, if $b$ is connected to $c$ and $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$. We call this sub-network $D_I$. In $D_I$, there is no compensating pair.
			\end{lemma}

@@

			Recall the sign function of nodes from Definition \ref{sign_of_nodes}. Because now we allow weak compensating paths, the sign function is no longer defined on all nodes.

@@

			\begin{lemma}
				If $c$ is in the next layer after $b$, $S(c)\neq 0, S(b)$ are both defined, and $W_{bc}\neq 0$, then $Sign(W_{bc})S(c)=S(b)$.
			\end{lemma}
